The \dealii{} Library, Version 9.3

### 2021-06-17 9.3/paper.tex
Remove old names.
Updates list of coauthors; introduces new Sec. 2.7 for candi

\newcommand{\specialword}[1]{\texttt{#1}}
\newcommand{\dealii}{{\specialword{deal.II}}\xspace}
\newcommand{\pfrst}{{\specialword{p4est}}\xspace}
\newcommand{\trilinos}{{\specialword{Trilinos}}\xspace}
\newcommand{\aspect}{\specialword{Aspect}\xspace}
\newcommand{\petsc}{\specialword{PETSc}\xspace}
\newcommand{\cmake}{{\specialword{CMake}}\xspace}
\newcommand{\autoconf}{{\specialword{autoconf}}\xspace}

@@

 \author[6,7]{Martin~Kronbichler}
 \affil[6]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch@lnm.mw.tum.de}}}
 \affil[7]{Department of Information Technology,
   Uppsala University,
   Box 337, 751\,05 Uppsala, Sweden.
   {\texttt{martin.kronbichler@it.uu.se}}}

\author[8]{Matthias~Maier}
\affil[8]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[6,9]{Peter Munch}
 \affil[10]{Institute of Materials Research, Materials Mechanics,
 Helmholtz-Zentrum Geesthacht,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

\author[10]{Jean-Paul~Pelteret}
\affil[10]{Independent researcher.
{\texttt{jppelteret@gmail.com}}}

% \author[12]{Reza Rastak}
% \affil[12]{Department of Civil and Environmental Engineering,
%   Stanford University,
%   Stanford, CA 94305, USA.
%   {\texttt{rastak@stanford.edu}}}

% \author[**13]{Ignacio Tomas}
% \affil[13]{Sandia National Laboratories, Org 1442,
% P.O. Box 5800, MS 1320, Albuquerque, NM, 87185-1320,
%   \texttt{itomas@sandia.gov}}

\author[1*]{Bruno~Turcksin}
%

%\author[14]{Zhuoran Wang}
%\affil[14]{Department of Mathematics, Colorado State University, Fort Collins,
%          CO 80523-1874, USA.
%{\texttt{zhrwang@math.colostate.edu}}}

\author[15]{David Wells}
\affil[15]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

>>>>

\newcommand{\specialword}[1]{\texttt{#1}}
\newcommand{\dealii}{{\specialword{deal.II}}\xspace}
\newcommand{\pfrst}{{\specialword{p4est}}\xspace}
\newcommand{\trilinos}{{\specialword{Trilinos}}\xspace}
\newcommand{\aspect}{\specialword{Aspect}\xspace}
\newcommand{\petsc}{\specialword{PETSc}\xspace}
\newcommand{\cmake}{{\specialword{CMake}}\xspace}
\newcommand{\candi}{{\specialword{candi}}\xspace}

@@

\author[6]{Uwe~K{\"o}cher}
\affil[6]{Chair of Numerical Mathematics,
  Helmut-Schmidt-University,
  University of the Federal Armed Forces Hamburg,
  Holstenhofweg~85, 22043 Hamburg, Germany.
  {\texttt{uwe.koecher@hsu-hh.de}}}

 \author[7,8]{Martin~Kronbichler}
 \affil[7]{Institute for Computational Mechanics,
   Technical University of Munich,
   Boltzmannstr.~15, 85748 Garching, Germany.
   {\texttt{kronbichler/munch@lnm.mw.tum.de}}}
 \affil[8]{Department of Information Technology,
   Uppsala University,
   Box 337, 751\,05 Uppsala, Sweden.
   {\texttt{martin.kronbichler@it.uu.se}}}

\author[9]{Matthias~Maier}
\affil[9]{Department of Mathematics,
  Texas A\&M University,
  3368 TAMU,
  College Station, TX 77845, USA.
  {\texttt{maier@math.tamu.edu}}}

\author[7,10]{Peter Munch}
 \affil[10]{Institute of Materials Research, Materials Mechanics,
 Helmholtz-Zentrum Geesthacht,
 Max-Planck-Str. 1, 21502 Geesthacht, Germany.
   {\texttt{peter.muench@hzg.de}}}

\author[11]{Jean-Paul~Pelteret}
\affil[11]{Independent researcher.
{\texttt{jppelteret@gmail.com}}}

\author[1*]{Bruno~Turcksin}

\author[16]{David Wells}
\affil[16]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Terminal based toolchain installer}
\label{subsec:candi}

Half a page up to a page on candi.
